Topic modeling on EU and the USA research projects

### 2017-06-20 thesis_report/draft_thesis.tex
Add: appendix

Many applications of topic modeling also eliminate from the vocabulary so-
called “stop” words. These are words that are common in most documents and do
not correspond to any particular subject matter. They include pronouns (you,
he, it), connectives (and, because, however), prepositions (to, of, before),
and auxiliaries (have, been, can, should). Stop words may also include generic
nouns (amount, part, nothing) and verbs (do, have). A collection of documents
is represented as a two-dimensional matrix where each row describes a document
and each column corresponds to a word. Each entry in this matrix is an integer
count; most entries are zero. It makes sense to view each column as a feature.

@@

In figure x we show the 10 topics that consists of the 20 top words with the
highest posterior probability of belonging to the topic. The size of each word
is in proportion to each probability; the bigger the word, the higher the
probability. Each wordcloud describes a topic, which we can find intuitevely.
Below are listed the topics that we found corresponding to the words that
describe them:
\begin{center}
\begin{figure}
\begin{tabular}{rcl}
\subfloat[Topic 0]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/EU_topic0_all.png}} &
\subfloat[Topic 1]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/EU_topic1_all.png}} &
\subfloat[Topic 2]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/EU_topic2_all.png}}\\
\subfloat[Topic 3]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/EU_topic3_all.png}} &
\subfloat[Topic 4]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/EU_topic4_all.png}} &
\subfloat[Topic 5]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/EU_topic5_all.png}}\\
\subfloat[Topic 6]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/EU_topic6_all.png}} &
\subfloat[Topic 7]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/EU_topic7_all.png}} &
\subfloat[Topic 8]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/EU_topic8_all.png}}\\
\subfloat[Topic 9]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/EU_topic9_all.png}} &
\end{tabular}
\caption{Wordclouds of topics of the EU dataset (1994-2017)}
\end{figure}
\end{center}

@@

>>>>

Many applications of topic modeling also eliminate from the vocabulary so
called “stop” words. These are words that are common in most documents and do
not correspond to any particular subject matter. They include pronouns (you,
he, it), connectives (and, because, however), prepositions (to, of, before),
and auxiliaries (have, been, can, should). Stop words may also include generic
nouns (amount, part, nothing) and verbs (do, have). A collection of documents
is represented as a two-dimensional matrix where each row describes a document
and each column corresponds to a word. Each entry in this matrix is an integer
count; most entries are zero. It makes sense to view each column as a feature.

@@

In figure x we show the 10 topics that consists of the 20 top words with the
highest posterior probability of belonging to the topic. The size of each word
is in proportion to each probability; the bigger the word, the higher the
probability. Each wordcloud describes a topic, which we can find intuitevely.
Below are listed the topics that we found corresponding to the words that
describe them:
\begin{center}
\begin{figure}
\begin{tabular}{rcl}
\subfloat[Topic 0]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/EU_topic0_all.png}} &
\subfloat[Topic 1]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/EU_topic1_all.png}} &
\subfloat[Topic 2]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/EU_topic2_all.png}}\\
\subfloat[Topic 3]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/EU_topic3_all.png}} &
\subfloat[Topic 4]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/EU_topic4_all.png}} &
\subfloat[Topic 5]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/EU_topic5_all.png}}\\
\subfloat[Topic 6]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/EU_topic6_all.png}} &
\subfloat[Topic 7]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/EU_topic7_all.png}} &
\subfloat[Topic 8]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/EU_topic8_all.png}}\\
\subfloat[Topic 9]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/EU_topic9_all.png}} &
\subfloat[Topic 10]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/EU_topic10_all.png}} &
\subfloat[Topic 11]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/EU_topic11_all.png}}\\
\end{tabular}
\caption{Wordclouds of topics of the EU dataset (1994-2017)}
\end{figure}
\end{center}

@@

\clearpage
\appendix

\begin{center}
\begin{figure}
\begin{tabular}{rcl}
\subfloat[Topic 0]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic0_7000.png}} &
\subfloat[Topic 1]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic1_7000.png}}&
\subfloat[Topic 2]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic2_7000.png}}\\
\subfloat[Topic 3]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic3_7000.png}}&
\subfloat[Topic 4]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic4_7000.png}} &
\subfloat[Topic 5]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic5_7000.png}}\\
\subfloat[Topic 6]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic6_7000.png}} &
\subfloat[Topic 7]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic7_7000.png}}&
\subfloat[Topic 8]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic8_7000.png}}\\
\subfloat[Topic 9]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic9_7000.png}}&
\end{tabular}
\caption{Wordclouds of topics of the EU FP4 (1994-1998)}
\end{figure}
\end{center}

\begin{center}
\begin{figure}
\begin{tabular}{rcl}
\subfloat[Topic 0]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic0_7000.png}} &
\subfloat[Topic 1]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic1_7000.png}}&
\subfloat[Topic 2]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic2_7000.png}}\\
\subfloat[Topic 3]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic3_7000.png}}&
\subfloat[Topic 4]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic4_7000.png}} &
\subfloat[Topic 5]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic5_7000.png}}\\
\subfloat[Topic 6]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic6_7000.png}} &
\subfloat[Topic 7]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic7_7000.png}}&
\subfloat[Topic 8]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic8_7000.png}}\\
\subfloat[Topic 9]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic9_7000.png}}&
\end{tabular}
\caption{Wordclouds of topics of the EU FP5 (1998-2002)}
\end{figure}
\end{center}

\begin{center}
\begin{figure}
\begin{tabular}{rcl}
\subfloat[Topic 0]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic0_7000.png}} &
\subfloat[Topic 1]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic1_7000.png}}&
\subfloat[Topic 2]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic2_7000.png}}\\
\subfloat[Topic 3]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic3_7000.png}}&
\subfloat[Topic 4]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic4_7000.png}} &
\subfloat[Topic 5]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic5_7000.png}}\\
\subfloat[Topic 6]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic6_7000.png}} &
\subfloat[Topic 7]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic7_7000.png}}&
\subfloat[Topic 8]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic8_7000.png}}\\
\subfloat[Topic 9]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic9_7000.png}}&
\end{tabular}
\caption{Wordclouds of topics of the EU FP6 (2002-2006)}
\end{figure}
\end{center}

\begin{center}
\begin{figure}
\begin{tabular}{rcl}
\subfloat[Topic 0]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic0_7000.png}} &
\subfloat[Topic 1]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic1_7000.png}}&
\subfloat[Topic 2]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic2_7000.png}}\\
\subfloat[Topic 3]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic3_7000.png}}&
\subfloat[Topic 4]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic4_7000.png}} &
\subfloat[Topic 5]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic5_7000.png}}\\
\subfloat[Topic 6]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic6_7000.png}} &
\subfloat[Topic 7]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic7_7000.png}}&
\subfloat[Topic 8]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic8_7000.png}}\\
\subfloat[Topic 9]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic9_7000.png}}&
\end{tabular}
\caption{Wordclouds of topics of the EU FP7 (2007-2013)}
\end{figure}
\end{center}

\begin{center}
\begin{figure}
\begin{tabular}{rcl}
\subfloat[Topic 0]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic0_20000.png}} &
\subfloat[Topic 1]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic1_20000.png}}&
\subfloat[Topic 2]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic2_20000.png}}\\
\subfloat[Topic 3]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic3_20000.png}}&
\subfloat[Topic 4]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic4_20000.png}} &
\subfloat[Topic 5]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic5_20000.png}}\\
\subfloat[Topic 6]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic6_20000.png}} &
\subfloat[Topic 7]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic7_20000.png}}&
\subfloat[Topic 8]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic8_20000.png}}\\
\subfloat[Topic 9]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic9_20000.png}}&
\end{tabular}
\caption{Wordclouds of topics of the EU H2020 (2014-2020)}
\end{figure}
\end{center}

\begin{center}
\begin{figure}
\begin{tabular}{rcl}
\subfloat[Topic 0]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic0_8000.png}} &
\subfloat[Topic 1]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic1_8000.png}}&
\subfloat[Topic 2]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic2_8000.png}}\\
\subfloat[Topic 3]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic3_8000.png}}&
\subfloat[Topic 4]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic4_8000.png}} &
\subfloat[Topic 5]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic5_8000.png}}\\
\subfloat[Topic 6]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic6_8000.png}} &
\subfloat[Topic 7]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic7_8000.png}}&
\subfloat[Topic 8]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic8_8000.png}}\\
\subfloat[Topic 9]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic9_8000.png}}&
\end{tabular}
\caption{Wordclouds of topics of the USA (1994-1997)}
\end{figure}
\end{center}

\begin{center}
\begin{figure}
\begin{tabular}{rcl}
\subfloat[Topic 0]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic0_8000.png}} &
\subfloat[Topic 1]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic1_8000.png}}&
\subfloat[Topic 2]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic2_8000.png}}\\
\subfloat[Topic 3]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic3_8000.png}}&
\subfloat[Topic 4]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic4_8000.png}} &
\subfloat[Topic 5]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic5_8000.png}}\\
\subfloat[Topic 6]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic6_8000.png}} &
\subfloat[Topic 7]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic7_8000.png}}&
\subfloat[Topic 8]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic8_8000.png}}\\
\subfloat[Topic 9]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic9_8000.png}}&
\end{tabular}
\caption{Wordclouds of topics of the USA (1998-2001)}
\end{figure}
\end{center}

\begin{center}
\begin{figure}
\begin{tabular}{rcl}
\subfloat[Topic 0]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic0_8000.png}} &
\subfloat[Topic 1]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic1_8000.png}}&
\subfloat[Topic 2]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic2_8000.png}}\\
\subfloat[Topic 3]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic3_8000.png}}&
\subfloat[Topic 4]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic4_8000.png}} &
\subfloat[Topic 5]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic5_8000.png}}\\
\subfloat[Topic 6]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic6_8000.png}} &
\subfloat[Topic 7]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic7_8000.png}}&
\subfloat[Topic 8]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic8_8000.png}}\\
\subfloat[Topic 9]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic9_8000.png}}&
\end{tabular}
\caption{Wordclouds of topics of the USA (2002-2006)}
\end{figure}
\end{center}

\begin{center}
\begin{figure}
\begin{tabular}{rcl}
\subfloat[Topic 0]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic0_9000.png}} &
\subfloat[Topic 1]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic1_9000.png}}&
\subfloat[Topic 2]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic2_9000.png}}\\
\subfloat[Topic 3]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic3_9000.png}}&
\subfloat[Topic 4]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic4_9000.png}} &
\subfloat[Topic 5]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic5_9000.png}}\\
\subfloat[Topic 6]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic6_9000.png}} &
\subfloat[Topic 7]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic7_9000.png}}&
\subfloat[Topic 8]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic8_9000.png}}\\
\subfloat[Topic 9]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic9_9000.png}}&
\end{tabular}
\caption{Wordclouds of topics of the USA (2007-2013)}
\end{figure}
\end{center}

\begin{center}
\begin{figure}
\begin{tabular}{rcl}
\subfloat[Topic 0]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic0_8000.png}} &
\subfloat[Topic 1]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic1_8000.png}}&
\subfloat[Topic 2]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic2_8000.png}}\\
\subfloat[Topic 3]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic3_8000.png}}&
\subfloat[Topic 4]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic4_8000.png}} &
\subfloat[Topic 5]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic5_8000.png}}\\
\subfloat[Topic 6]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic6_8000.png}} &
\subfloat[Topic 7]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic7_8000.png}}&
\subfloat[Topic 8]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic8_8000.png}}\\
\subfloat[Topic 9]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic9_8000.png}}&
\end{tabular}
\caption{Wordclouds of topics of the USA (2014-2017)}
\end{figure}
\end{center}
